Corpus stage 3

### 2020-12-15 analysis/corpus-stage3.Rmd
changes!

---
title: "Kaggle stage2"
output: html_document
params:
  base_dir: /var/lib/R/project-evalR
editor_options: 
  chunk_output_type: console
---

@@

```{r loading raw data}
kaggle_kernels <- as_tibble(read_fst(KAGGLE_KERNELS_FILE))
kaggle_log <- as_tibble(read_fst(KAGGLE_LOG_FILE)) %>%
  transmute(
    id=str_replace(Command, ".*/kaggle-run/[^/]+/([^/]+)/.*", "\\1"),
    exitval=Exitval,
    runtime=as.duration(JobRuntime)
  )
```

### Programs

```{r}
kaggle_programs <- left_join(
  kaggle_kernels,
  kaggle_log,
  by="id"
) %>%
  mutate(
    file=path("../../run/kaggle-run", competition, id, "calls.fst"),
    corpus="kaggle"
  ) %>%
  select(
    file,
    id,
    language,
    kernel_type,
    competition,
    runtime,
    code,
    exitval,
    corpus
  )

kaggle_programs_errors <- 
  kaggle_programs %>%
  mutate(
    error_file=path(dirname(str_replace(file, fixed("../.."), params$base_dir)), "calls-ERROR"), 
    error=file.exists(error_file)
  ) %>%
  filter(error) %>%
  rowwise() %>%
  do(mutate(read_fst(.$error_file), file=.$file))

kaggle_programs <-
    left_join(
      kaggle_programs, 
      if (nrow(kaggle_programs_errors) > 0) {
        transmute(kaggle_programs_errors, error=paste(source, message, call), file)
      } else {
        transmute(kaggle_programs, error=NA, file)
      }, 
      by="file"
    ) %>%
    mutate(
      success=
        exitval==0 &
        !is.na(code) &
        !is.na(runtime) &
        code > 0 &
        is.na(error)
    )
```

```{r}
write_fst(kaggle_programs, KAGGLE_PROGRAMS_FILE)
```

>>>>

---
title: "Corpus stage 3"
output: html_document
params:
  base_dir: /var/lib/R/project-evalR
editor_options: 
  chunk_output_type: console
---

@@

```{r}
calls       <- read_fst(CALLS_FILE) %>% mutate(package=basename(dirname(dirname(file))))
corpus      <- read_fst(CORPUS_DETAILS_FILE)
calls_final <- semi_join(calls, corpus, by="package")
```

```{r export data}
write_fst(calls_final, "../../run/package-evals-traced/calls-final.fst")
```
